Stochastic Variance-Reduced Policy Gradient

### 2018-02-07 svrpg.tex
Auto stash before merge of "master" and "origin/master"
corrections on section 5.3

\subsection{Baseline}
As reported in Sec. \ref{subsec:PolicyGradient} a known method for variance reduction in Reinforcement Learning is the use of baseline.
This method is independent to SVRPO.
We decide to test SVRPO with an Actor Critic baseline: the baseline is a states dependent linear function with a time-varying feature vector \cite{duan2016benchmarking}.
Our choice is to use a single baseline for each term of expression \ref{E:svrpg.estimate.batch}. This is update only in the snapshot: the baseline is estimated using the N trajectories.

>>>>

\subsection{Baseline}
As reported in Sec. \ref{subsec:PolicyGradient} a well known variance reduction tool in Reinforcement Learning is the baseline.
This tool does not depend on SVRPO. More precicely we decided to use an Actor Critic baseline, which is a state dependent linear function with a time-varying feature vector \cite{duan2016benchmarking}. Furthermore, the baseline is unique and computed every snapshot using the N trajectories at hand.
